Screening Sinkhorn Algorithm for Regularized Optimal Transport

### 2019-05-21 tex/v3/section_3_algorithm.tex
new section 3

\paragraph{Static screening test.} The core of the static screening test developed in this work aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and 
$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the L-BFGS-B solver.
Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.

@@

Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained L-BFGS-B for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}).$ 
The L-BFGS-B solver handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.

>>>>

\paragraph{Static screening test.} The core of the static screening test developed in this paper aims at locating two subsets of indices $(I, J)$ in $\{1, \ldots, n\}\times\{1, \ldots, m\}$ satisfying: $e^{u_i}\geq \alpha_u, \text{ and } e^{v_j}\geq \alpha_v, \text{ for all } (i,j) \in I \times J$ and 
$e^{u_{i'}} = \alpha_u, \text{ and } e^{v_{j'}} = \alpha_v, \text{ for all } (i',j') \in I^\complement \times J^\complement$, namely $(u,v) \in \mathcal{C}^n_{\alpha_u}\times \mathcal{C}^m_{\alpha_v}$.
The sets $I$ and $J$ are called active sets, we further emphasize that they are determined in an initialization step in the proposed algorithm before running the LBFGS solver.
Consequently, we can work on a "screened" dual of Sinkhorn divergence by considering variables that belong only to $\R^{|I|} \times \R^{|J|}$ in order to reduce the computational cost.

@@

Pseudocode of our proposed algorithm is shown in Algorithm~\ref{screenkhorn}. %~\cite{nocedal1980,nocedal2006numerical}
It is worth to note that Screenkhorn algorithm uses only the restricted parts $K_{(I_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})},$ $K_{(I_{\varepsilon,\kappa}, J^\complement_{\varepsilon,\kappa})},$ and $K_{(I^\complement_{\varepsilon,\kappa}, J_{\varepsilon,\kappa})}$ of the Gibbs kernel $K$ for calculating the objective function $\Psi_{\varepsilon, \kappa}$ and its gradients, in contrast to Sinkhorn algorithm which performs alternating updates of all rows and columns of $K.$
Furthermore, it consists of two steps: the first one is an initialization providing the active sets $I_{\varepsilon,\kappa}$, $J_{\varepsilon,\kappa}$. 
The second is a constrained LBFGS for the stacked variable $\theta=(u_{I_{\varepsilon,\kappa}},v_{J_{\varepsilon,\kappa}}),$ 
that handles box constraints on variables, and it becomes more efficient when these box bounds are carefully determined for problem~\eqref{screen-sinkhorn_second_def}. 
The following proposition (proof in supplementary material) expresses these bounds that are pre-calculated in the initialization step of Screenkhorn.
